### 2018-11-09 Writeup/PERT_New.tex
Change the solver to Cplex

	In our problem, we assume at most one stochastic disruption can occur at a random time in the project span. We also assume for each activity \(i \in I\), the crashing decision for that activity needs to be made at the start of that activity, and cannot be changed afterwards. The disruption does not affect the started activities but changes the length of those that have not started according to a random distribution. It is usually hard to compute the recourse function directly when parameters are distributed according to continuous distributions, and therefore SAA is proposed to approximate the problem by a large-scale deterministic optimization problem with a finite scenario set \cite{kim2015guide,shapiro2009lectures}. In this paper, we assume there is a discrete finite set of scenarios indexed by \(\omega \in \Omega\). For each scenario \(\\omega\), the random realization of parameters, \(\xi^\omega\), consists of the timing of disruption, \(H\), and the changed duration of each activity, \(d_i, \forall i \in I\). \\

@@

\section{Experimental Results} \label{sec:results}
%	\textcolor{blue}{Test results:
%	\begin{itemize}
%		\item Describe the test examples: where do they come from, number of nodes, how are they generated.
%		\item Cite Sen's paper and describe the implementation.
%		\item Results.
%	\end{itemize}}
	In this section, we address the following questions with our computational results:
	\begin{enumerate}
		\item What is the value of model~\eqref{prob:extensive} that takes account of randomness in both timing and magnitude of a disruption? In other words, what are other alternative solutions that are easier to obtain but possibly inferior? How does quality of the solution to model~\eqref{prob:extensive} compare to those alternative solutions?
		\item How does the solution quality improve as the number of samples used in sample average approximation increases? 
		\item What is the time improvement of Algorithm~\ref{alg:Cut} compared to solving extensive formulation~\eqref{prob:extensive} using state-of-the-art MIP solvers? Other algorithms solving 2SMIP with mixed binary recourse?
	\end{enumerate}
	We first introduce the PERT network used for test and distribution information used to characterize uncertainty in Section~\ref{subsec:example}. In Section~\ref{subsec:value} we construct a series of deterministic and semi-deterministic alternatives to model~\eqref{prob:extensive}, perform out-of-sample tests, and present the better quality result of solution to model~\eqref{prob:extensive} compared to the alternative ones. We test the effect of different simulation budgets on solution quality and computational performance in Section~\ref{subsec:budget}. Finally in Section~\ref{subsec:time} we present the computational advantage of Algorithm~\ref{alg:Cut} compared to solving extensive formulation and the ancestral Benders decomposition method (\textcolor{blue}{Cite Sen's two papers}.)\\
	\newline
	All tests are run on a server with 20 Intel Xeon cores at 3.1 GHz and 256 GB of RAM. All models are constructed using version 0.18.0 of the JuMP package \cite{DunningHuchetteLubin2017} on the Julia platform. All linear programs and mixed integer programs are solved by Gurobi 8.01 \cite{gurobi2016} with default parameters.

	\subsection{Test Cases Construction} \label{subsec:example}
	\subsection{Value of a Fully Stochastic Model} \label{subsec:value}
	In this section, we first construct a deterministic problem assuming no disruption occurs and three semi-deterministic alternatives assuming: both timing and magnitude of the disruption are random, only the timing is random, and only the magnitude is random.
	\subsection{Simulation Budget} \label{subsec:budget}
	\subsection{Computational Performance} \label{subsec:time}
\bibliographystyle{plain}
\bibliography{PERT_Bib}

>>>>

	In our problem, we assume at most one stochastic disruption can occur at a random time in the project span. We also assume for each activity \(i \in I\), the crashing decision for that activity needs to be made at the start of that activity, and cannot be changed afterwards. The disruption does not affect the started activities but changes the length of those that have not started according to a random distribution. It is usually hard to compute the recourse function directly when parameters are distributed according to continuous distributions, and therefore SAA is proposed to approximate the problem by a large-scale deterministic optimization problem with a finite scenario set \cite{kim2015guide,shapiro2009lectures}. In this paper, we assume there is a discrete finite set of scenarios indexed by \(\omega \in \Omega\). For each scenario \(\omega\), the random realization of parameters, \(\xi^\omega\), consists of the timing of disruption, \(H\), and the changed duration of each activity, \(d_i, \forall i \in I\). \\

@@

\section{Experimental Results} \label{sec:results}
%	\textcolor{blue}{Test results:
%	\begin{itemize}
%		\item Describe the test examples: where do they come from, number of nodes, how are they generated.
%		\item Cite Sen's paper and describe the implementation.
%		\item Results.
%	\end{itemize}}
	In this section, we address the following questions with our computational results:
	\begin{enumerate}
		\item What is the value of model~\eqref{prob:extensive} that takes account of randomness in both timing and magnitude of a disruption? In other words, what are other alternative solutions that are easier to obtain but possibly inferior? How does quality of the solution to model~\eqref{prob:extensive} compare to those alternative solutions?
		\item How does the solution quality improve as the number of samples used in sample average approximation increases? 
		\item What is the time improvement of Algorithm~\ref{alg:Cut} compared to solving extensive formulation~\eqref{prob:extensive} using state-of-the-art MIP solvers? Other algorithms solving 2SMIP with mixed binary recourse?
	\end{enumerate}
	We first introduce the PERT network used for test and distribution information used to characterize uncertainty in Section~\ref{subsec:example}. In Section~\ref{subsec:value} we construct a series of deterministic and semi-deterministic alternatives to model~\eqref{prob:extensive}, perform out-of-sample tests, and present the better quality result of solution to model~\eqref{prob:extensive} compared to the alternative ones. We test the effect of different simulation budgets on solution quality and computational performance in Section~\ref{subsec:budget}. Finally in Section~\ref{subsec:time} we present the computational advantage of Algorithm~\ref{alg:Cut} compared to solving extensive formulation.\\
	%  and the ancestral Benders decomposition method (\textcolor{blue}{Cite Sen's two papers}.)
	\newline
	All tests are run on a server with 20 Intel Xeon cores at 3.1 GHz and 256 GB of RAM. All models are constructed using version 0.18.0 of the JuMP package \cite{DunningHuchetteLubin2017} on the Julia platform. All linear programs and mixed integer programs are solved by \textcolor{blue}{CPLEX} with both the feasibility tolerance and the integrality tolerance as \(10^{-7}\). We refer interested readers to \textcolor{blue}{GitHub repository} for the input data and the code used in this paper. %Gurobi 8.01 \cite{gurobi2016}

	\subsection{Test Cases Construction} \label{subsec:example}
%	\textcolor{blue}{Where we find our tests:
%		\begin{itemize}
%			\item Plambeck paper: Case 11
%			\item V42: Case 14
%			\item Case 19 from Elmgrabhy
%			\item Case 55 from Elmgrabhy
%			\item Randomized network 75, 100 nodes
%			\item Plambeck paper: Case 110
%	\end{itemize}}
	\noi Although it is easy to construct an activity network with randomly distributed disruption time and magnitude, not all instances constructed can well illustrate properties of our problem. Therefore, we construct our test cases based on the activity networks used in the previous literature, which have been shown of research value. We use two activity networks from \textcolor{blue}{Plambeck et al.}, one with 11 activities and the other with 110 activities. We also take two examples from Elmgrabhy \cite{Elmaghraby77}, one with 19 activities and the other with 55 activities. We manually create one activity network with 14 activities and generate two random networks with 75 and 100 activities, respectively using \textcolor{blue}{RanGen toolbox}. In the following section, we use ``Case \(X\)" to denote the test case with \(X\) activities.\\
	\newline
	For every test case, the timing of disruption follows a lognormal distribution since its value has to be nonnegative. The disruption magnitude of activities follows an exponential distribution of which the parameter differs among activities. The exponential distribution can best model the drastic change caused by a disruption.
	\subsection{Simulation Budget} \label{subsec:budget}
	We first examine the quality of solutions generated from different sizes of samples. It is well known that the objective value obtained by SAA approaches the objective function of the original problem as the sample size grows to infinity, and the expected value of the SAA objective value improves as the sample size increases~\cite{shapiro2009lectures}. However, when the sample size increases, the computational cost increases as well. Understanding how the solution quality changes according to different sample sizes is important to help us decide a proper sample size while achieving a decent solution. For each test case in Section~\ref{subsec:example}, we first obtain \(20\) batches of the optimal solution to model~\ref{prob:extensive} by Algorithm~\ref{alg:Cut}, with sample sizes \(n = 10, 50, 100, 200, 500\) and \(1000\). For each of those solutions, we test against a set of \(5000\) samples and obtain the object value. We compare the 
	\subsection{Value of a Fully Stochastic Model} \label{subsec:value}
	In this section, we compare the quality of five solutions obtained under different possible problem settings to show the value of modeling both the random timing and magnitude of the disruption. First, we can solve a deterministic project crashing problem assuming no disruption occurs (denoted as ``DET"). Three semi-stochastic alternatives can be constructed assuming: both timing and magnitude of the disruption are deterministic at their expected values (denoted as ``EXP"), the timing is random but the magnitude is at its expected value (denoted as ``\(H\)Only"), and the magnitude is random but the timing is at its expected value (denoted as ``\(d\)Only"). Finally, we construct the full stochastic model where both the timing and the magnitude are random (denoted as ``FULL"). 
	\subsection{Computational Performance} \label{subsec:time}
\bibliographystyle{plain}
\bibliography{PERT_Bib}
